Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-02-16 doc/main_jfm.tex

\ReviewerOne{An empirical numerical study found that for the baseline
parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
so that the membrane ruptured whenever $\chi > \chi_*$ and did not
rupture whenever $\chi < \chi_*.$ Supplementary Materials Movie 4 shows
the membrane rupture at the critical shear rate.  To further quantify
the competition between shear and attraction, we found that a $5 \%$
relative increase in the parameters $\gamma$ and $M$ resulted in a $4.24
\%$ relative increase in $\chi_*$, from $0.0655$ to $0.0688$.  A $5 \%$
decrease in the particle radius $c$, screening length $\rho$ gave a
$-9.55 \%$ decrease, $5.0 \%$ increase respectively in $\chi_*$.
Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
decrease in critical shear rate $\chi_*$.}  
  \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.7$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
  \[
  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}

>>>>

\ReviewerOne{An empirical numerical study found that for the baseline
parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
so that the membrane ruptured whenever $\chi > \chi_*$ and did not
rupture whenever $\chi < \chi_*.$ Supplementary Materials Movie 4 shows
the membrane rupture at the critical shear rate.  To further quantify
the competition between shear and attraction, we found that a $5 \%$
relative increase in the parameters $\gamma$ and $M$ resulted in a $4.24
\%$ relative increase in $\chi_*$, from $0.0655$ to $0.0688$.  A $5 \%$
decrease in the particle radius $c$, screening length $\rho$ gave a
$-9.55 \%$ decrease, $5.0 \%$ increase respectively in $\chi_*$.
Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
decrease in critical shear rate $\chi_*$.}  
  \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 
  \begin{equation}
    \label{eq:CSR}
  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
  \end{equation}
  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.7$
  so that surface forces are comparable to viscous forces.  
  There is a related \emph{elastic} capillary number
  $\widetilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
  used to characterize rheological properties of lipid bilayer membranes
  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
  Setting $\text{Ca}$ and $\widetilde{\text{Ca}}$ equal, we can derive
  \[
  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
  \]
  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
